Using CopyKAT to identify tumor cells in Ewing sarcoma samples

### 2024-07-09 analyses/cell-type-ewings/template_notebooks/cnv-workflow/01-marker-genes.Rmd
move cnv output

---
title: "Manual classification of tumor cells"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  results_dir: "annotate_tumor_cells_output"
  reference_cell_file: "reference-cells.tsv"
---

@@

```{r}
project_root <- here::here()
renv::load(project_root)
```

>>>>

---
title: "Manual classification of tumor cells"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  results_dir: "cnv_annotation"
  reference_cell_file: "reference-cells.tsv"
---

@@

```{r}
project_root <- here::here()
renv::load(project_root)

knitr::opts_chunk$set(
  dev = "jpeg"
)
```

### 2024-07-09 analyses/cell-type-ewings/template_notebooks/cnv-workflow/02-cellassign.Rmd
move cnv output

---
title: "Explore tumor cell classification with CellAssign"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  tumor_marker_predictions: "tumor-marker_predictions.tsv"
  visser_marker_predictions: "visser-all-marker_predictions.tsv"
  panglao_predictions: "panglao-endo-fibro_predictions.tsv"
  results_dir: "annotate_tumor_cells_output"
---

>>>>

---
title: "Explore tumor cell classification with CellAssign"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  tumor_marker_predictions: "tumor-marker_predictions.tsv"
  visser_marker_predictions: "visser-all-marker_predictions.tsv"
  panglao_predictions: "panglao-endo-fibro_predictions.tsv"
  results_dir: "cnv_annotation"
---

### 2024-07-09 analyses/cell-type-ewings/template_notebooks/cnv-workflow/03-copykat.Rmd
move cnv output

---
title: "Using CopyKAT to identify tumor cells in Ewing sarcoma samples"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  no_ref_copykat_results: "copykat/no_reference"
  with_ref_copykat_results: "copykat/with_reference"
  reference_cell_file: ".reference-cells.tsv"
  results_dir: "annotate_tumor_cells_output"
---

>>>>

---
title: "Using CopyKAT to identify tumor cells in Ewing sarcoma samples"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  no_ref_copykat_results: "copykat/no_reference"
  with_ref_copykat_results: "copykat/with_reference"
  reference_cell_file: ".reference-cells.tsv"
  results_dir: "cnv_annotation"
---
